### 2020-04-27 README.Rmd
docu badge

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.com/c1au6i0/covid19census.svg?branch=master)](https://travis-ci.com/c1au6i0/covid19census)
[![Codecov test coverage](https://codecov.io/gh/c1au6i0/covid19census/branch/master/graph/badge.svg)](https://codecov.io/gh/c1au6i0/covid19census?branch=master)
<!-- badges: end -->
